---
output:
  github_document:
    html_preview: false
---


# Waveform analysis

## Running waveform analysis

After setting up the analysis tools, commandline interface should be avaible.

For standard scope data (non-digitizer runs), the SSRL routine can be used to perform waveform analysis:

```{r, engine='bash', eval=FALSE}
run_Ana --selector SSRL --directory path_to_raw_wavforms_root_files --config ssrl_ana_config.yaml
```

The `--selector` picks the implemented analysis routine. There are also other quick analysis routine to perform simple check during the beam test (TODO). The `ssrl_ana_config.yaml` fine tune the metthods and setting for the `SSRL` analysis routine, e.g. baseline correction etc.

The `ssrl_ana_config.yaml` contains the following:

```{r echo=FALSE, results='asis'}
cat(paste0("```","YAML","\n"))
cat(readLines('../configs/AnaSSRL_2024_March_FBK_RSD.yaml', warn=FALSE), sep = '\n')
cat("\n```\n")
```

## Running quick heatmap for scan runs

Heatmap of pmax can be quickly generated for scan runs with the following:

```{r, engine='bash', eval=FALSE}
run_Ana --selector QuickScan --directory <path_to_scan_root_files> --config </configs/heatmap.yaml>
```